\begin{abstract}
Data sets gathered from large-scale sensor networks are often prone to suffer from a significant fraction of missing data due to issues such as communication interference, power depletion, or hardware failure. 
Many standard data analysis tools are ill-equipped to deal will missing values, hence the need to impute missing readings prior to analysis.
We have developed novel imputation methods which takes a ``Recommendation Systems'' view of the problem: the sensors and their readings at each time step are viewed as users and product ratings with the goal of estimating the missing ratings.
Sensor readings differ from product ratings in that the former exhibit high correlation in both time and space.
To incorporate this property, we utilize Matrix and Tensor Factorization common in the Recommendation Systems domain and augment the formulations to support temporal and spatial relationships in the data.
We evaluate the approaches using two different environmental sensor network datasets, one indoor and one outdoor.
We show that a temporally-biased MF significantly outperforms standard MF.
In addition, our experimental results show that our methods also outperform hybrid-kNN and linear interpolation.
Interestingly, incorporation of a spatial information into the formulation is shown to be ineffective to be ineffective for our datasets as the MF-based approach is already able to discover such correlations among sensors.
Finally, we extend the approach to include possible correlations between different sensor types (e.g., temperature and humidity) on the same sensor node.
Our results show...
\end{abstract}
